%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
\usepackage[T1]{fontenc}
\usepackage[default]{sourcesanspro}
% other options kept for reference:
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage{CormorantGaramond}
% \usepackage{charter}

% Slightly looser line spacing for readability
\linespread{1.08}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{2pt}\raggedright\large\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-2pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{1pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{2pt}\item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \bfseries Dilshan Wickramasinghe} \\ \vspace{2pt}
    \small Matara, Sri Lanka \\ \vspace{2pt}
    \small \raisebox{-0.1\height}\faPhone\ +94 77 10 22 972 \quad
    \href{mailto:dilshanmw717@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{dilshanmw717@gmail.com}} \quad
    \href{https://linkedin.com/in/dilshanwix717}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}} \quad
    \href{https://github.com/dilshanwix717}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} \quad
    \href{https://dilshan-dev.vercel.app/}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}}
    \vspace{-8pt}
\end{center}


%-----------PROFILE-----------
\section{Profile}
\small{Full-stack engineer with 2 years of experience developing production web applications, streaming platforms, and real-time web games at CeylonX and D B International Technology. Work spans  \textbf{NestJS and Node.js} backend services,  \textbf{React and Next.js} frontends, and  \textbf{Cocos Creator} game clients, backed by  \textbf{PostgreSQL, MySQL and MongoDB} and   \textbf{AWS}.}
\vspace{-4pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Ruhuna}{2020 -- Dec. 2025}
      {Bachelor of Computer Science}{Matara, Sri Lanka}
    \resumeSubheading
      {Rahula College Matara}{}{GCE Advanced Level -- Mathematics: A $|$ Physics: C $|$ Chemistry: C}{Matara, Sri Lanka}
    \resumeSubheading
      {National Photographic Art Society of Sri Lanka}{}
      {Diploma in Photography}{}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {D B International Technology}{Apr. 2025 -- Present}
      {Associate Software Engineer}{Sri Lanka}
      \resumeItemListStart
        \resumeItem{Full-stack engineer on a team developing web-based gaming platforms and casino games.}
        \resumeItem{Contributed to the \textbf{Digital Scratch Card} ticket game across backend and game client --- built a ticket-generation engine with weight-table validation that produced exact winning and losing distributions to protect RTP, regenerating on validation failure and returning tickets instantly to the player; extended into a batch pipeline that generated \textasciitilde{}\textbf{130M} tickets into \textbf{PostgreSQL. \emph{NestJS, TypeORM, PostgreSQL, Cocos Creator.}}}
        \resumeItem{Contributed to a \textbf{Gaming Platform} with a micro-service backend --- an API gateway fronting separate account and lobby services over \textbf{RabbitMQ}, deployed on \textbf{Kubernetes} for concurrent players; worked on auth proxying, lobby routing (games, vendors, categories), and edge rate-limiting.\textbf{ \emph{NestJS, RabbitMQ, PostgreSQL, Kubernetes.}}}
        \resumeItem{Contributed to the \textbf{Gaming Platform} frontend --- a \textbf{Next.js} (React) + \textbf{Tailwind CSS} player client (lobby, game browsing, wallet, account) and a separate admin panel consuming the gateway APIs.\textbf{ \emph{Next.js, React.js, Tailwind CSS, TypeScript.}}}
        \resumeItem{Contributed to \textbf{Chicken Road Crash}, a real-time multiplier crash game where players bet and cash out before a live multiplier crashes --- built the \textbf{Cocos Creator} game client using a Finite State Machine (FSM) architecture, calling backend endpoints via the built-in Fetch API for bet creation, crash-point checks, cash-outs, and auth; the \textbf{NestJS} backend broadcast round state over \textbf{Socket.IO} with \textbf{RabbitMQ} for event fan-out.\textbf{ \emph{NestJS, Socket.IO, RabbitMQ, PostgreSQL, Cocos Creator.}}}

      \resumeItemListEnd

    \resumeSubheading
      {CeylonX Corporation}{Dec. 2024 -- Mar. 2025}
      {Associate Software Engineer}{Sri Lanka}
      \resumeItemListStart
        \resumeItem{Full-stack engineer on a team developing subscription-based streaming platforms and corporate web products.}
        \resumeItem{Contributed to \textbf{Susila}, a Sri Lankan subscription streaming platform, with a \textbf{React} web client, \textbf{Node.js} API, and an admin panel for catalog and subscription management; delivered video over \textbf{HLS (m3u8)} with \textbf{Vimeo} as the origin to scale to many concurrent viewers, and integrated \textbf{Stripe} for recurring subscriptions and \textbf{Firebase Cloud Messaging} for push notifications.}
        \resumeItem{Contributed to the \textbf{CeylonX corporate website and admin portal} --- a \textbf{React} marketing site with a \textbf{Three.js} 3D globe and animated sections, backed by a \textbf{Node.js}/\textbf{Express} and \textbf{MongoDB} API covering blog, portfolio, careers, testimonials, and project requests; added a \textbf{TinyMCE} admin so non-technical editors could manage all content themselves.}
        \resumeItem{Deployed services to \textbf{AWS} with GitHub-triggered CI/CD, owning pre-prod to prod rollouts end-to-end.}
      \resumeItemListEnd

    \resumeSubheading
      {CeylonX Corporation}{Jun. 2024 -- Dec. 2024}
      {Intern Software Engineer}{Sri Lanka}
      \resumeItemListStart
        \resumeItem{Full-stack intern across production client projects using React.js, Node.js, MongoDB, MySQL, Firebase, and PayHere.}
        \resumeItem{Contributed to \textbf{Rainbow Swimming Club's online-payment app} end-to-end --- a \textbf{React} + \textbf{MUI} client with a \textbf{Node.js}/\textbf{Express} and \textbf{MySQL} backend that lets members pay membership and class fees online through \textbf{PayHere} (Sri Lanka's major payment gateway); implemented the full MD5-signed redirect and server-to-server notify-webhook flow with signature verification, status-code checks, idempotent success lookups, admin notifications, and printable receipts.}
        \resumeItem{Contributed features and maintenance to a production \textbf{restaurant POS system} running at Iluk Restaurant \& Bar and Savour Street --- worked across the \textbf{React} frontend, admin dashboard, and \textbf{Node.js} backend APIs for order entry, menu management, and auth.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-6pt}


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{NestJS Microservices: API Gateway + Auth + User} $|$ \emph{NestJS, TypeScript, RabbitMQ, PostgreSQL, Redis}}{}
      \resumeItemListStart
        \resumeItem{Self-initiated for a streaming-platform backbone --- API gateway fronting independent Auth and User services over \textbf{RabbitMQ}, idempotency keys, and domain-event fan-out; per-service \textbf{circuit breakers}, exponential-backoff retries, and \textbf{Redis} caching.}
        \resumeItem{\textbf{RS256 JWT} , \textbf{Argon2id} password hashing, \textbf{device fingerprinting} with session-family token-reuse detection, per-endpoint \textbf{rate limiting}, and account lockout; \textbf{Prometheus} metrics + \textbf{Jaeger} distributed tracing.}
        \resumeItem{\faGithub\ \href{https://github.com/dilshanwix717/API-Gateway-NestJS}{\underline{API Gateway}} $|$ \href{https://github.com/dilshanwix717/Auth-Service-NestJS}{\underline{Auth Service}} $|$ \href{https://github.com/dilshanwix717/User-Service-NestJS}{\underline{User Service}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Home Cinema --- E-commerce Streaming App} $|$ \emph{React, Vite, TypeScript, Node.js, Firebase, HLS}}{}
      \resumeItemListStart
        \resumeItem{Full-stack movie e-commerce platform --- users purchase individual titles and stream them over HLS. \textbf{ReactJS + TypeScript client, Node.js API with Firebase} and \textbf{Stripe} for payment handling, and a separate ReactJS admin panel for catalog, payment, and user management.}
        \resumeItem{\faGithub\ \href{https://github.com/dilshanwix717/Movie-App-Frontend}{\underline{Frontend}} $|$ \href{https://github.com/dilshanwix717/Movie-app-backend}{\underline{Backend}} $|$ \href{https://github.com/dilshanwix717/Movie-App-admin}{\underline{Admin Panel}}}
      \resumeItemListEnd

    \resumeProjectHeading
      {\textbf{Online HLS Video Player} $|$ \emph{Next.js, TypeScript, HLS.js, Vercel}}{}
      \resumeItemListStart
        \resumeItem{Browser-based HLS video player built on \textbf{Next.js + HLS.js} that streams \textbf{.m3u8} manifests with adaptive playback.}
        \resumeItem{\faGithub\ \href{https://github.com/dilshanwix717/online-video-player}{\underline{GitHub Repository}}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-6pt}


%
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript} \\
     \textbf{Frameworks \& Libraries}{: React.js, Next.js, Tailwind CSS, Node.js, NestJS} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, MySQL, Firebase} \\
     \textbf{Infrastructure \& Cloud}{: AWS, Docker, CI/CD (GitHub Actions), RabbitMQ, Redis, Linux, macOS, Windows} \\
     \textbf{Game Development}{: Cocos Creator} \\
     \textbf{Tools}{:  Postman, Figma, Trello} \\
     \textbf{Working Knowledge}{:  Spring Boot, ASP.NET Core, Laravel, PHP, Kubernetes, Kafka, Unity, Godot, Networking} \\
    }}
 \end{itemize}
 \vspace{-6pt}


%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AWS Educate -- Introduction to Cloud} $|$ \emph{Amazon Web Services}}{}
          \resumeItemListStart
            \resumeItem{\href{https://www.credly.com/badges/228aaed7-0f46-4d78-97ab-9dab3ec99dfa/public\_url}{\underline{View Credential on Credly}}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd
\vspace{-6pt}


%-----------INVOLVEMENT---------------
\section{Leadership \& Activities}
    \resumeSubHeadingListStart
        \resumeSubheading{Science Faculty Football Team}{2023}{Captain}{University of Ruhuna}
            \resumeItemListStart
                \resumeItem{Led the faculty squad and also represented the University of Ruhuna football team at \textbf{SLUG XIV 2023} (Sri Lanka University Games).}
            \resumeItemListEnd
        \resumeSubheading{Science Faculty Sports Club}{2023 -- 2024}{Senior Editor}{University of Ruhuna}
            \resumeItemListStart
                \resumeItem{Led end-to-end editorial workflow for club publications during the 2023–2024 academic year, overseeing content planning, commissioning, review, and timely delivery across the Sports Club calendar.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------REFERENCES-----------
% References are hidden by default. To re-enable, remove the \begin{comment} / \end{comment} wrapper below.
\begin{comment}
\section{References}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Ms. Binuri Raigamkorale}{binuriyr@dcs.ruh.ac.lk $|$ +94 71 908 2273}
      {Lecturer, Department of Computer Science}{University of Ruhuna}
    \resumeSubheading
      {Mr. L.L. Gihan Chathuranga}{gihan@dcs.ruh.ac.lk $|$ +94 77 659 2307}
      {Lecturer, Department of Computer Science}{University of Ruhuna}
  \resumeSubHeadingListEnd
\end{comment}


\end{document}
