%-------------------------
% 1-page Resume — Dilshan Wickramasinghe
% Condensed version of the full CV. For a longer, more detailed version,
% see Dilshan_Wickramasinghe_CV.tex (2 pages).
% Template based on: https://github.com/sb2nov/resume  (MIT)
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT----------
\usepackage[T1]{fontenc}
\usepackage[default]{sourcesanspro}

\linespread{1.04}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins — slightly wider horizontal, tighter vertical
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.85in}
\addtolength{\textheight}{1.7in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{1pt}\raggedright\large\bfseries
}{}{0em}{\MakeUppercase}[\color{black}\titlerule \vspace{-3pt}]

\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{1pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \vspace{1pt}\item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-5pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}


\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \bfseries Dilshan Wickramasinghe} \\ \vspace{2pt}
    \small Matara, Sri Lanka \\ \vspace{2pt}
    \small \raisebox{-0.1\height}\faPhone\ +94 77 10 22 972 \quad
    \href{mailto:dilshanmw717@gmail.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{dilshanmw717@gmail.com}} \quad
    \href{https://linkedin.com/in/dilshanwix717}{\raisebox{-0.2\height}\faLinkedin\ \underline{LinkedIn}} \quad
    \href{https://github.com/dilshanwix717}{\raisebox{-0.2\height}\faGithub\ \underline{GitHub}} \quad
    \href{https://dilshan-dev.vercel.app/}{\raisebox{-0.2\height}\faGlobe\ \underline{Portfolio}}
    \vspace{-8pt}
\end{center}


%-----------PROFILE-----------
\section{Profile}
\small{Full-stack engineer with 2 years of experience developing production web applications, streaming platforms, and real-time web games at CeylonX and D B International Technology. Work spans \textbf{NestJS} and \textbf{Node.js} backend services, \textbf{React} and \textbf{Next.js} frontends, and \textbf{Cocos Creator} game clients, backed by \textbf{PostgreSQL}, \textbf{MySQL}, and \textbf{MongoDB} on \textbf{AWS}.}
\vspace{-4pt}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Ruhuna}{2020 -- Dec. 2025}
      {Bachelor of Computer Science}{Matara, Sri Lanka}
    \resumeSubheading
      {Rahula College Matara}{}{GCE Advanced Level -- Mathematics: A $|$ Physics: C $|$ Chemistry: C}{Matara, Sri Lanka}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {D B International Technology}{Apr. 2025 -- Present}
      {Associate Software Engineer}{Sri Lanka}
      \resumeItemListStart
        \resumeItem{Contributed to the \textbf{Digital Scratch Card} ticket game --- built a ticket-generation engine with weight-table validation producing exact winning and losing distributions to protect RTP; extended into a batch pipeline that generated \textasciitilde{}130M tickets into \textbf{PostgreSQL}. \emph{NestJS, TypeORM, Cocos Creator.}}
        \resumeItem{Contributed to a \textbf{Gaming Platform} with a micro-service backend --- API gateway fronting account and lobby services over \textbf{RabbitMQ}, deployed on \textbf{Kubernetes}; worked on auth proxying, lobby routing, and edge rate-limiting.}
        \resumeItem{Contributed to the \textbf{Gaming Platform} frontend --- a \textbf{Next.js} + \textbf{Tailwind CSS} player client (lobby, wallet, account) and a separate admin panel, in \textbf{TypeScript}, consuming the gateway APIs.}
        \resumeItem{Contributed to \textbf{Chicken Road Crash}, a real-time multiplier crash game --- built the \textbf{Cocos Creator} game client using a Finite State Machine (FSM) architecture; the \textbf{NestJS} backend broadcast round state over \textbf{Socket.IO} with \textbf{RabbitMQ} for event fan-out.}
      \resumeItemListEnd

    \resumeSubheading
      {CeylonX Corporation}{Dec. 2024 -- Mar. 2025}
      {Associate Software Engineer}{Sri Lanka}
      \resumeItemListStart
        \resumeItem{Contributed to \textbf{Susila}, a Sri Lankan subscription streaming platform with a \textbf{React} client and \textbf{Node.js} API; delivered video over \textbf{HLS (m3u8)} with \textbf{Vimeo} as origin, integrated \textbf{Stripe} for subscriptions and \textbf{Firebase Cloud Messaging} for push.}
        \resumeItem{Contributed to the \textbf{CeylonX corporate website and admin portal} --- a \textbf{React}/\textbf{Three.js} frontend with a \textbf{Node.js}/\textbf{Express} and \textbf{MongoDB} API, \textbf{TinyMCE} admin for non-technical editors; deployed on \textbf{AWS} with GitHub-triggered CI/CD.}
      \resumeItemListEnd

    \resumeSubheading
      {CeylonX Corporation}{Jun. 2024 -- Dec. 2024}
      {Intern Software Engineer}{Sri Lanka}
      \resumeItemListStart
        \resumeItem{Contributed to \textbf{Rainbow Swimming Club's online-payment app} --- a \textbf{React} + \textbf{MUI} client with a \textbf{Node.js}/\textbf{Express} and \textbf{MySQL} backend; implemented the full \textbf{PayHere} MD5-signed redirect and notify-webhook flow with signature verification, idempotent lookups, and printable receipts.}
        \resumeItem{Contributed features and maintenance to a production \textbf{restaurant POS system} running at Iluk Restaurant \& Bar and Savour Street --- worked across the \textbf{React} frontend and \textbf{Node.js} backend APIs. Promoted to Associate after 6 months.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-4pt}


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{NestJS Microservices: API Gateway + Auth + User} $|$ \emph{NestJS, TypeScript, RabbitMQ, PostgreSQL, Redis}}{}
      \resumeItemListStart
        \resumeItem{Self-initiated 3-service streaming-platform backbone over RabbitMQ with dead-letter queues, idempotency, and domain-event fan-out; gateway with per-service circuit breakers, Redis caching, Prometheus metrics, and Jaeger tracing.}
        \resumeItem{RS256 JWT (15-min access + 7-day opaque refresh), Argon2id hashing, device-fingerprinted session-reuse detection, per-endpoint rate limits, account lockout.}
        \resumeItem{\faGithub\ \href{https://github.com/dilshanwix717/API-Gateway-NestJS}{\underline{API Gateway}} $|$ \href{https://github.com/dilshanwix717/Auth-Service-NestJS}{\underline{Auth Service}} $|$ \href{https://github.com/dilshanwix717/User-Service-NestJS}{\underline{User Service}}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{-4pt}


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: TypeScript, JavaScript} \\
     \textbf{Frameworks \& Libraries}{: React.js, Next.js, Tailwind CSS, Node.js, NestJS, Cocos Creator} \\
     \textbf{Databases}{: PostgreSQL, MongoDB, MySQL, Firebase} \\
     \textbf{Infrastructure \& Cloud}{: AWS, Docker, CI/CD (GitHub Actions), RabbitMQ, Redis, Linux, macOS, Windows} \\
     \textbf{Tools}{: Figma, Postman, Trello} \\
     \textbf{Working Knowledge}{: Java, C\#, C, PHP, Spring Boot, ASP.NET Core, Laravel, Kubernetes, Kafka, MS SQL, Unity, Godot, Networking} \\
    }}
 \end{itemize}
 \vspace{-4pt}


%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{AWS Educate -- Introduction to Cloud} $|$ \emph{Amazon Web Services} $|$ \href{https://www.credly.com/badges/228aaed7-0f46-4d78-97ab-9dab3ec99dfa/public\_url}{\underline{View on Credly}}}{}
    \resumeSubHeadingListEnd

\end{document}
